ShrinkNets

### 2018-01-04 paper/paper.tex
Writing pass up to Related Work

To demonstrate that the approach is viable, we will first show that Shrinking
Networks converge. For this experiment we trained a one hidden layer neural
network with one filter layer to control the number of hidden units. We
initialized the models with $10000$ neurons and trained them on \texttt{MNIST}
using different regularization factors ($\lambda$). We summarized the results in
\autoref{convergence_plot}. [Should we explain the results ?] \srm{Yes, you need
to explain in detail -- what does this show?  How does it prove that your
approach works / is a good idea?}

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{convergence}
\caption{Evolution of the number of hidden units and loss over time on the \texttt{MNIST} dataset for different $\lambda$ values \label{convergence_plot}}
\end{center}
\end{figure}

@@

\subsection{Comparison between Shrinking and classic Networks}

To demonstrate the value of ShrinkNets in the context of hyper-parameter
optimization we set up the following experiment: We consider two different
architectures, a three hidden layer feed forward network and a \textit{LeNet-5}
[ref]. We do not know the number of channels and neurons and we want to find the
best architecture by performing random search on the parameters that define the
size. For classic neural networks these parameters are the number of channels
and/or neurons; for ShrinkNets there is only one parameter, $\lambda$. We
sampled 50 models of each and trained them, picked the best epoch according to
the validation accuracy and measured their performance on the testing set. Since
ShrinkNets can be considered to be regularized in some sense, to make the
comparison fair we also considered static networks with an $L2$ regularization
factor (also drawn randomly) \srm{L2 regularization over what?}. We summarized
the accuracy we obtained on \autoref{hyper_opt_res}. [Should we explain the
results] \srm{Yes, need to describe in detail -- how does this prove that your
method works/ is a good idea?  What are the key takeaways?}

>>>>

To demonstrate that the approach is viable, we will first show that Shrinking
Networks converge properly. For this experiment we trained a one hidden layer
neural network with one filter layer to control the number of hidden units. We
initialized the models with $10000$ neurons and trained them on \texttt{MNIST}
using different regularization factors ($\lambda$). We summarized the results
in \autoref{convergence_plot}. We can see on this plot is that
for a given $\lambda$ the number of hidden units seems to always converge to
some value. It has two implications: it seems that $\lambda$ is, as we would think,
a proxy of the network size (bigger $\lambda$ imply smaller networks). Secondly,
it indicates that the spikes we see in the regular spikes we see in the loss that occur when neurons are disabled will eventually disapear because the number of neurons reach a plateau. \gl{I feel we should give a conclusion for this paragraph but
I am not sure what to say}
\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{convergence}
\caption{Evolution of the number of hidden units and loss over time on the \texttt{MNIST} dataset for different $\lambda$ values \label{convergence_plot}}
\end{center}
\end{figure}

\subsection{Relevance in the context of hyper-parameter optimization}

\gl{I rewrote the entire section}

One of our main goal is to help finding neural network architectures that
perform reasonably well faster than existing techniques. For simplicity,
we will try to see how ShrinkNets perform when doing random search. However,
we believe that the results generalize to more complex methods, most of them
might actually benefit a lot from the reduction in the dimensionality of the
hyper-parameter space.

\par To isolate the effect of ShrinkNets we will consider very simple architectures
We will be using multi-layer perceptrons (with three hidden layers) and
convolutional neural networks (With the LeNet-5 architecture). For this experiment
we will assume we have no information about the size except an upper bound of
$50$ channels per convolutional layer and $5000$ neuron for fully connected layers.
We try to find the appropriate size of the network using classical neural networks
and ShrinkNets. To make sure that we are as fair as possible and since one might
argue that ShrinkNets is also regularizing the network in addition to finding the
size, we will also considered regualrized classic networks using the most commonly
used technique the $L_2$ penalty [ref].
\par The experiment consist in sampling parameters randomly for each class of
network, train them for the same amount of epochs (100 for MLPs and 200 for CNNs). Pick the epoch that performed the best on the validation accuracy and evaluate it
on the testing set. We repeat the process for 50 models. This evaluation was done
on \texttt{MNIST} [ref], \texttt{FashionMNIST} [ref] and \texttt{CIFAR10} [ref]. The distribution of the testing accuracy we obtained is summarized on \autoref{hyper_opt_res}.

We can see that the distributions for ShrinkNets are consistently better than the
others for all datasets and both architectures. It shows that by training fewer
networks, we are likely to obtain on-par or even better models which effectively
reduces the cost of hyper-parameter optimization. In some cases the best ShrinkNets
models outperforms the best model of the other techniques.

@@
